Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-21 manuscript.Rmd
exemplar timeline

@@

metric_plot <- function(ds, met) {
  ds %>% filter(metric == met) %>% 
    ggplot(aes(x = Model, y = value)) + 
    geom_sina(alpha = .7, fill = "aquamarine3", size = 4, maxwidth = .5, shape = 21) +
    stat_summary(fun = "mean", mapping = aes(x = Model, y = value), shape = "-", fill = "black", size = 4) + 
    ylim(0, 1) + ylab(met) + xlab("") + 
    theme(plot.title.position = "plot",
          axis.title.y = element_text(size = 13),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 13))
}
metric_labels <- c("Overall Accuracy", "Balanced Accuracy", "F1", "Sensitivity", "Pos Pred Value", "Kappa")
title_labels <- c("A. Overall Accuracy", "B. Balanced Accuracy", "C. F1 Score", "D. Sensitivity", "E. Pos. Pred. Value", "F. Kappa")
metric_plots <- map(metric_labels, ~ metric_plot(metrics_long, .x)) %>% map2(., title_labels, ~.x + ggtitle(.y))
(metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])/(metric_plots[[5]] + metric_plots[[6]])

@@

difference_plot <- function(ds) {
  ds <- mutate(ds, diff = prop_human - prop_model)
  ggplot(filter_outliers(ds), aes(x = pos, y = diff, fill = pos, group = file)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = -.1, ymax = .1, fill = "darkgray", color = "darkgray") + 
  #geom_rect(aes(xmin = "Held", xmax = "Upright",ymin = -.1, ymax = .1), fill = "#e5e5e5", color = "#e5e5e5") + 
  stat_summary(data = filter(ds, file %in% outlier_files), position = position_dodge(.4), aes(shape = file), fill = "#333333", size = .75, stroke = .25) +
  stat_summary(position = position_dodge(.4), shape = 21, size = .75, stroke = .25) +
  scale_fill_manual(values = pal, guide = "none") +
  scale_shape_manual(guide = "none", values = 22:24) + 
  coord_cartesian(ylim = c(-1, 1)) + xlab("") + 
  scale_y_continuous(name = "Prediction Difference (min)", breaks = seq(-1, 1, .2), labels = seq(-10, 10, 2), minor_breaks = waiver()) + 
    theme(axis.text.x = element_text(size = 13, color = "black"))
}
difference_plots <- map(agree_bins, ~ difference_plot(.x))
difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
difference_plots[[1]] + difference_plots[[2]]
```

>>>>

```{r exemplartimeline, out.width="0.9\\linewidth", include=TRUE, fig.align="center", fig.cap="Example Timeline Caption.", echo=FALSE}
knitr::include_graphics("figures/timeline.png")
# Generated from analysis-pt2/methods-exemplar-agreement.R
# Annotated in illustrator based on event times:
# Exemplar participant is 120-1
# > pt2_start_time
# [1] "2022-11-13 11:11:00 PST"
# > pt2_end_time
# [1] "2022-11-13 12:41:01 PST"
# > session_param$start_time_coded
# [1] "2022-11-13 10:02:40 PST"
```

@@

metric_plot <- function(ds, met) {
  ds %>% filter(metric == met) %>% 
    ggplot(aes(x = Model, y = value)) + 
    geom_sina(alpha = .7, fill = "turquoise3", size = 4, maxwidth = .5, shape = 21) +
    stat_summary(fun = "mean", mapping = aes(x = Model, y = value), shape = "-", fill = "black", size = 4) + 
    ylim(0, 1) + ylab(met) + xlab("") + 
    theme(plot.title.position = "plot",
          axis.title.y = element_text(size = 13),
          axis.text.y = element_text(size = 11),
          axis.text.x = element_text(size = 13))
}
metric_labels <- c("Overall Accuracy", "Balanced Accuracy", "F1", "Sensitivity", "Pos Pred Value", "Kappa")
title_labels <- c("A. Overall Accuracy", "B. Balanced Accuracy", "C. F1 Score", "D. Sensitivity", "E. Pos. Pred. Value", "F. Kappa")
metric_plots <- map(metric_labels, ~ metric_plot(metrics_long, .x)) %>% map2(., title_labels, ~.x + ggtitle(.y))
(metric_plots[[1]] + metric_plots[[2]])/(metric_plots[[3]]+metric_plots[[4]])/(metric_plots[[5]] + metric_plots[[6]])

@@

difference_plot <- function(ds) {
  ds <- mutate(ds, diff = prop_human - prop_model)
  ggplot(filter_outliers(ds), aes(x = pos, y = diff, fill = pos, group = file)) +
  annotate("rect", xmin = -Inf, xmax = Inf, ymin = -.1, ymax = .1, fill = "gray", color = "gray") + 
  #geom_rect(aes(xmin = "Held", xmax = "Upright",ymin = -.1, ymax = .1), fill = "#e5e5e5", color = "#e5e5e5") + 
  stat_summary(data = filter(ds, file %in% outlier_files), position = position_dodge(.4), aes(shape = file), fill = "#333333", size = .75, stroke = .25) +
  stat_summary(position = position_dodge(.4), shape = 21, size = .75, stroke = .25) +
  scale_fill_manual(values = pal, guide = "none") +
  scale_shape_manual(guide = "none", values = 22:24) + 
  coord_cartesian(ylim = c(-1, 1)) + xlab("") + 
  scale_y_continuous(name = "Prediction Difference (min)", breaks = seq(-1, 1, .2), labels = seq(-10, 10, 2), minor_breaks = waiver()) + 
    theme(axis.text.x = element_text(size = 13, color = "black"))
}
difference_plots <- map(agree_bins, ~ difference_plot(.x))
difference_plots <- map2(difference_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
difference_plots[[1]] + difference_plots[[2]]
```
